Modeling and analyzing the Corona-virus warning app with the Isabelle Infrastructure framework

### 2020-07-11 paper.tex
"the German app" -> "CWA"

%The CWA
%has taken a long time to develop being published only on
%16th June 2020. It
%was a quite costly project but this was mainly due to the management of
%Telekom and SAP being in the driving seat. But the app has been designed with great
The app was designed with great
attention on privacy: a distributed architecture \cite{cwa:arch} has been adopted %after a long and
%heated debate with supporters of a central architecture. The distributed architecture is
that is
based on a very clever application design whereby clients broadcast
highly anonymized so called ``Ephemeral IDs'' via Bluetooth and
store those ids of people in close proximity.
%highly anonymized so called ``Ephemeral IDs'' at physical locations via the
%Bluetooth Low Energy Beacon protocol.
%The app saves those ids of people in close proximity.
Infected persons report their infection by uploading their ids to a central server, providing all clients the means to assess exposure risk locally,
hence, stored contact data has never to be shared.
%Infected persons report their infection to a central server,
%which, in turn, provides all clients the means to reconstruct the ids
%used by reported cases over the last 14 days.
%
%When at a later date an infected person reports his infection to a central server,
%all clients are provided the means to reconstruct the ids used by this particular
%person's device over the last 14 days.
%Therefore, exposure risks can be evaluated locally and stored contact data has never to be shared.
%
%, the unique root ID is published
%and in the daily check all mobile phones connecting to the central server download
%the root IDs of infected people. Since the Ephemeral IDs can be mapped to the root ID
%all Ephemeral IDs that have been saved over the last 14 days allow users' phones to
%regularly check whether their user has been exposed to an infected person and issue
%a warning to the user and recommendation to contact health authorities.
%The warning issued by the Corona warning app entitles to
%having a Corona test done (which at the time of writing is not normally possible).

@@

In this paper, we first provide some background in Section \ref{sec:background}:
we give a brief overview of related works
and the protocol of the German app (Section \ref{sec:history}).
We then introduce the Isabelle Infrastructure framework (Section \ref{sec:isainf}).
Next, we present our model (Section \ref{sec:model}) and analysis of privacy and
attacks (Section \ref{sec:ana}). The found attack on the first abstract specification
motivates refinement. The formal definition of refinement for the Isabelle Infrastructure
framework is introduced and illustrated on the CWA (Section \ref{sec:ref})
before drawing some conclusions (Section \ref{sec:concl}).

>>>>

%The CWA
%has taken a long time to develop being published only on
%16th June 2020. It
%was a quite costly project but this was mainly due to the management of
%Telekom and SAP being in the driving seat. But the app has been designed with great
The app was designed with great
attention on privacy: a distributed architecture \cite{cwa:arch} has been adopted %after a long and
%heated debate with supporters of a central architecture. The distributed architecture is
that is
based on a very clever application design whereby clients broadcast
highly anonymized so called ``Ephemeral Ids'' via Bluetooth and
store those ids of people in close proximity.
%highly anonymized so called ``Ephemeral IDs'' at physical locations via the
%Bluetooth Low Energy Beacon protocol.
%The app saves those ids of people in close proximity.
Infected persons report their infection by uploading their ids to a central server, providing all clients the means to assess exposure risk locally,
hence, stored contact data has never to be shared.
%Infected persons report their infection to a central server,
%which, in turn, provides all clients the means to reconstruct the ids
%used by reported cases over the last 14 days.
%
%When at a later date an infected person reports his infection to a central server,
%all clients are provided the means to reconstruct the ids used by this particular
%person's device over the last 14 days.
%Therefore, exposure risks can be evaluated locally and stored contact data has never to be shared.
%
%, the unique root ID is published
%and in the daily check all mobile phones connecting to the central server download
%the root IDs of infected people. Since the Ephemeral IDs can be mapped to the root ID
%all Ephemeral IDs that have been saved over the last 14 days allow users' phones to
%regularly check whether their user has been exposed to an infected person and issue
%a warning to the user and recommendation to contact health authorities.
%The warning issued by the Corona warning app entitles to
%having a Corona test done (which at the time of writing is not normally possible).

@@

In this paper, we first provide some background in Section \ref{sec:background}:
we give a brief overview of related works
and the protocol of CWA (Section \ref{sec:history}).
We then introduce the Isabelle Infrastructure framework (Section \ref{sec:isainf}).
Next, we present our model (Section \ref{sec:model}) and analysis of privacy and
attacks (Section \ref{sec:ana}). The found attack on the first abstract specification
motivates refinement. The formal definition of refinement for the Isabelle Infrastructure
framework is introduced and illustrated on the CWA (Section \ref{sec:ref})
before drawing some conclusions (Section \ref{sec:concl}).
